Choose a License

### 2025-01-26 about.qmd
Various minor improvements
Also mention bibliography file

cat(c("Quarto:", as.character(quarto::quarto_version())))
```

```{r}
#| class.output: "txt code-overflow-scroll"

@@

The file `Manuscript.qmd` is made available by Josephine Zerna and Christoph Scheffel under [CC0\ 1.0](LICENSE-CC0.txt).

>>>>

cat(paste0("Quarto ", as.character(quarto::quarto_version()), " was utilized to render the files."))
```

```{r}
#| class-output: "txt code-overflow-scroll"

@@

The files `Manuscript.qmd` and `Bibliography.bib` are made available by Josephine Zerna and Christoph Scheffel under [CC0\ 1.0](LICENSE-CC0.txt).

### 2025-01-26 choose_license.qmd
Also mention bibliography file

The manuscript you downloaded for this tutorial is made available to you under [CC0\ 1.0](https://creativecommons.org/publicdomain/zero/1.0/) as is all code in this tutorial (e.g., for creating the data dictionary). Therefore, you can apply any license to your modified version. Please apply the license of your choice now, using any of the methods mentioned above (except the `README`, which we will cover later).

@@

In the following example, the edited manuscript files have been multi-licensed under [AGPLv3](https://www.gnu.org/licenses/agpl-3.0.html) (or later) or (at option of the reuser) under [CC\ BY-SA\ 4.0](https://creativecommons.org/licenses/by-sa/4.0/), while the data dictionary and its code are made available under CC0\ 1.0.

@@

The data dictionary (stored in "data_dictionary.html") and the code used to create it (stored in "create_data_dictionary.R") by Florian Kohrt and <YOUR NAME> are available under CC0 1.0 <https://creativecommons.org/publicdomain/zero/1.0/>.
```

>>>>

The manuscript and the bibliography file you downloaded for this tutorial are made available to you under [CC0\ 1.0](https://creativecommons.org/publicdomain/zero/1.0/) as is all code in this tutorial (e.g., for creating the data dictionary). Therefore, you can apply any license to your modified version. Please apply the license of your choice now, using any of the methods mentioned above (except the `README`, which we will cover later).

@@

In the following example, the edited manuscript files have been multi-licensed under [AGPLv3](https://www.gnu.org/licenses/agpl-3.0.html) (or later) or (at option of the reuser) under [CC\ BY-SA\ 4.0](https://creativecommons.org/licenses/by-sa/4.0/), while the bibliography, the data dictionary and its code are made available under CC0\ 1.0.

@@

The bibliography (stored in "Bibliography.bib"), data dictionary (stored in "data_dictionary.html"), and the code used to create it (stored in "create_data_dictionary.R") by Florian Kohrt and <YOUR NAME> are available under CC0 1.0 <https://creativecommons.org/publicdomain/zero/1.0/>.
```
